---
title: "COFFEE APP STRUCTURE SHEET"
subtitle: "Explore the best ever coffee experience."
author: "Takahiro Hashimoto"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_section: true
    toc_float: true
    theme: paper
    code_folding: show
  pdf_document:
    toc: true
    number_section: true
always_allow_html: true
params:
  test: "test"
---

```{r base setting, include=FALSE}
library(DiagrammeR) # For mermaid
library(DT) # Interactive data table
library(ggplot2) # Basic plotting
library(plotly) # Interactive plotting
library(leaflet)
```


------------------------------------------------------------------------


# Sequence

```{r flowchart, echo=FALSE}
DiagrammeR::mermaid("
  graph TD
    subgraph Get Beans
      Get{Get Beans}-->|Add Info|Bn((lstBeans))
    end
    Bn-->|When Green Beans|Roast{Roast Beans}
    subgraph Roast Beans
      Roast-->|Add Info|Rt((tsRoasting))
    end
      Rt-->|Add Info|Bn
    subgraph Brewing
      Brew{Brewing}-->|Add Info|Br((tsBrewing))
      Bn-->|Merge Info|Br
    end
    subgraph Analytics
    Br-->|Create Prediction Models|prd[Prediction<br><br>Models]
    Br-->|Plot PCA|pca[Principal<br>Component<br> Analysis]
    pca-->|Check Models|prd
    end
    prd-->|Suggestion for<br>a Better Brewing|Brew
    ")
```

# Methodology {.tabset}

## Prediction Model
Using simple OLS.<br>
Note however that this might lead to indigenous, so better to use Instrumental variables.
$$
y_{brt}=\sum_{\{I|I=b,r,d\}}^i{w_ix_i} + \epsilon_{brt}  \\
y:Taste, \space b:Beans,\space r:Roasting, \space t:Time, \space d:Dripping, \space \epsilon:Error
$$ 

## Classification Model
Using Principal Component Analysis (PCA).<br>
Plot the results and check also the indigenous between variables especially with roastings and beans.

# Data Sets {.tabset}

## lstBeans
| variable | type |
| -------- | ---- |
| uid | strings |
| date.get | date |
| store | string |
| condition | boolean [1:roasted, 0:green]| 
| country | string| 
| grade | string| 
| variety | string| 
| notes | strings| 
| to.update | strings| 
| expired | boolean| 

## tsRoasting
| variable | type |
| -------- | ---- |
| uid | strings |
| date | date |
| beans | data frame from [lstBeans] | 
| condition | ordered integer [1:light, 3:medium, 5:dark]| 
| seconds | integer| 
| notes | strings: how to roast| 
| to.update | strings| 
| expired | boolean| 

## tsBrewing
| variable | type |
| -------- | ---- |
| uid | strings |
| date | date |
| timing | ordered integer [1:morning, 2:noon, 3:afternoon, 4:night, 5:midnight]| 
| roasting | data frame from [tsRoasting] | 
| pour.count | integer| 
| pour.seconds.total | integer| 
| pour1.seconds | integer| 
| pour1.gram | decimal| 
| pour2.seconds | integer| 
| pour2.gram | decimal| 
| pour3.seconds | integer| 
| pour3.gram | decimal| 
| pour4.seconds | integer| 
| pour4.gram | decimal| 
| pour5.seconds | integer| 
| pour5.gram | decimal| 
| pour6.seconds | integer| 
| pour6.gram | decimal| 
| pour7.seconds | integer| 
| pour7.gram | decimal| 
| pour8.seconds | integer| 
| pour8.gram | decimal| 
| taste | ordered integer [1:bad, 3:normal, 5:excellent]| 
| notes | strings| 
| to.update | strings| 
| expired | boolean| 

# Notes
- Before exporting as pdf, follow the lines below. Skipping this line will lead to errors when exporting pdf.
  - Run `tinytex::install_tinytex| | ` in console.
  - Add `always_allow_html: true` in YAML